Journal and article coverage

### 2024-11-12 analysis/results.Rmd
Compare uptake

```{r, knitr_setup, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center",
  dpi = 300
)
options(scipen = 999, digits = 4)
knitr::knit_hooks$set(
  inline = function(x) {
    if (is.numeric(x)) {
      return(prettyNum(x, big.mark = ","))
    } else{
      return(x)
    }
  }
)
```

@@

# Set themes for plots
my_base_size = 12

@@

```{r plot_uptake}
# Data prep
uptake_by_year <- uptake_df |>
  group_by(earliest_year, src) |>
  summarize(
    n_articles = sum(n_articles),
    n_oa_articles = sum(n_oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

uptake_by_year_df <- uptake_by_year |>
  # Remove HOAD because we only have first author data available
  filter(src != "HOAD") |>
  pivot_longer(cols = c(ta_oa_first_author_articles, ta_oa_corresponding_author_articles))

hoad_panel <- uptake_by_year |>
  filter(src == "HOAD") |>
  ggplot(aes(x = earliest_year)) +
  geom_bar(
    aes(y = n_oa_articles / n_articles, fill = "All"),
    stat = "identity",
    color = "#000000"
  ) +
  geom_bar(
    aes(y = ta_oa_first_author_articles / n_articles, fill = "TA OA"),
    stat = "identity",
    color = "#000000"
  ) +
  geom_text(
    aes(
      label = paste0(
        round(ta_oa_first_author_articles / n_oa_articles * 100, 1),
        "%\n(",
        format(ta_oa_first_author_articles, big.mark = ","),
        ")"
      ),
      y = ta_oa_first_author_articles / n_articles),
    position = position_dodge(width = 1),
    vjust = -0.2,
    # https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/
    size = 0.8 * my_base_size / .pt
  ) +
  scale_fill_manual(
    values = c("#b3b3b3a0", "#56B4E9"),
    name = "",
    guide = guide_legend(reverse = TRUE)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.05)),
    labels = scales::percent_format(),
    limits = c(0, .20),
    breaks = c(0, .05, .1, .15, .20)
  ) +
  theme_minimal(base_size = my_base_size) +
  labs(y = "Hybrid OA Uptake", x = NULL) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    axis.text.x = element_blank()
  )

wos_scp_uptake_panel <- uptake_by_year_df |>
  distinct(earliest_year, n_oa_articles, n_articles, src, name, value) |>
  # Modify factor levels to control order
  mutate(
    src = factor(src, levels = c("Scopus", "Web of Science")),
    name = factor(name, 
                 levels = c("ta_oa_first_author_articles", "ta_oa_corresponding_author_articles"))
  ) |>
  ggplot() +
  geom_bar(
    aes(
      x = earliest_year,
      y = n_oa_articles / n_articles,
      fill = "All"
    ),
    stat = "identity",
    color = "#000000"
  ) +
  geom_bar(
    aes(
      x = earliest_year,
      y = value / n_articles,
      fill = "TA OA"
    ),
    stat = "identity",
    color = "#000000"
  ) +
   geom_text(
    aes(
      label = paste0(
        round(value / n_oa_articles * 100, 1),
        "%\n(",
        format(value, big.mark = ","),
        ")"
      ),
      x = earliest_year,
      y = value / n_articles),
    position = position_dodge(width = 1),
    vjust = -0.2,
    # https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/
    size = 0.8 * my_base_size / .pt
  ) +
  facet_grid(fct_rev(src) ~ name) +
  scale_fill_manual(
    values = c("#b3b3b3a0", "#56B4E9"),
    name = "",
    guide = guide_legend(reverse = TRUE)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.05)),
    labels = scales::percent_format(),
    limits = c(0, .20),
    breaks = c(0, .05, .1, .15, .20)
  ) +
  theme_minimal(base_size = my_base_size) +
  labs(y = "Hybrid OA Uptake", x = NULL) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    axis.text.x = element_blank())
```

>>>>

```{r, knitr_setup, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "99%",
  fig.align = "center",
  dpi = 300
)
options(scipen = 999, digits = 4)
knitr::knit_hooks$set(
  inline = function(x) {
    if (is.numeric(x)) {
      return(prettyNum(x, big.mark = ","))
    } else{
      return(x)
    }
  }
)
```

@@

# Set themes for plots
my_base_size = 10

@@

```{r plot_uptake, fig.width=8}
# Data prep
uptake_by_year <- uptake_df |>
  mutate(earliest_year = as.character(earliest_year)) |>
  group_by(earliest_year, src) |>
  summarize(
    n_articles = sum(n_articles),
    n_oa_articles = sum(n_oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

uptake_by_year_df <- uptake_by_year |>
  # Remove HOAD because we only have first author data available
  filter(src != "HOAD", earliest_year != "2018") |>
  pivot_longer(cols = c(ta_oa_first_author_articles, ta_oa_corresponding_author_articles))

hoad_panel <- uptake_by_year |>
  filter(src == "HOAD") |>
  ggplot(aes(x = earliest_year)) +
  geom_bar(
    aes(y = n_oa_articles / n_articles, fill = "All"),
    stat = "identity",
    color = "#000000"
  ) +
  geom_bar(
    aes(y = ta_oa_first_author_articles / n_articles, fill = "TA OA"),
    stat = "identity",
    color = "#000000"
  ) +
  geom_text(
    aes(
      label = paste0(
        round(ta_oa_first_author_articles / n_oa_articles * 100, 1),
        "%\n(",
        format(ta_oa_first_author_articles, big.mark = ","),
        ")"
      ),
      y = ta_oa_first_author_articles / n_articles),
    position = position_dodge(width = 1),
    vjust = -0.2,
    # https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/
    size = 0.8 * my_base_size / .pt
  ) +
  scale_fill_manual(
    values = c("#b3b3b3a0", "#56B4E9"),
    name = "",
    guide = guide_legend(reverse = TRUE)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.05)),
    labels = scales::percent_format(),
    limits = c(0, .20),
    breaks = c(0, .05, .1, .15, .20)
  ) +
  theme_minimal(base_size = my_base_size) +
  labs(y = "Hybrid OA Uptake", x = NULL) +
  theme(
    legend.position = "top",
    legend.justification = "left"
  )

# Prepare facet labels
my_facet_labels <- c(ta_oa_first_author_articles = "First Author",
                  ta_oa_corresponding_author_articles = "Corresponding Author",
                  `Web of Science` = "Web of Science",
                  `Scopus` = "Scopus"
                )

wos_scp_uptake_panel <- uptake_by_year_df |>
  distinct(earliest_year, n_oa_articles, n_articles, src, name, value) |>
  # Modify factor levels to control order
  mutate(
    src = factor(src, levels = c("Web of Science", "Scopus")),
    name = factor(name, 
                 levels = c("ta_oa_first_author_articles", "ta_oa_corresponding_author_articles"))
  ) |>
  ggplot() +
  geom_bar(
    aes(
      x = earliest_year,
      y = n_oa_articles / n_articles,
      fill = "All"
    ),
    stat = "identity",
    color = "#000000"
  ) +
  geom_bar(
    aes(
      x = earliest_year,
      y = value / n_articles,
      fill = "TA OA"
    ),
    stat = "identity",
    color = "#000000"
  ) +
   geom_text(
    aes(
      label = paste0(
        round(value / n_oa_articles * 100, 1),
        "%\n(",
        format(value, big.mark = ","),
        ")"
      ),
      x = earliest_year,
      y = value / n_articles),
    position = position_dodge(width = 1),
    vjust = -0.2,
    # https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/
    size = 0.8 * my_base_size / .pt
  ) +
  facet_grid(src ~ name, labeller = as_labeller(my_facet_labels)) +
  scale_fill_manual(
    values = c("#b3b3b3a0", "#56B4E9"),
    name = "",
    guide = guide_legend(reverse = TRUE)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.05)),
    labels = scales::percent_format(),
    limits = c(0, .20),
    breaks = c(0, .05, .1, .15, .20)
  ) +
  theme_minimal(base_size = my_base_size) +
  labs(y = "Hybrid OA Uptake", x = NULL) +
  theme(
    legend.position = "top",
    legend.justification = "left")

## Combine to patchwork
layout <- "
AC
BB
"
wrap_plots(
  A = hoad_panel,
  B = wos_scp_uptake_panel,
  C = guide_area(),
  design = layout,
  guides = "collect",
  axes = "collect",
  heights = c(0.5, 1)
) &
  theme(
    legend.position = "top",
    legend.justification = "right",
    legend.direction = "horizontal",
 #   panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "grey50", fill = NA),
    axis.title=element_text(size = 10)) &
    plot_annotation(tag_levels = 'A')
